Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-04-27 Grassmannian_cells.tex
Minor edits in Section 4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique. On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$. In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_k)$ with $j_i\leq n$ and $k\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k-1},u_{m-k})$. For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $k\leq n-1$, there exist exact sequences of the form
\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]

Using this notation, we obtain the following lemma:
\begin{lemma}
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal. 
    \item All nontrivial proper subrepresentations of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement should directly follow from \cite{gab} and the fact that $F_Q$ is a covering functor (precise reference). The second part follows for instance recursively by applying BGP-reflections.

@@

\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k})}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
where the vertical maps are injective. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not. Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason. Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom does not split.
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

\end{proof}
If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$.

\begin{lemma}\label{directsums}
  If each $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ has a cell decomposition into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$.
\end{lemma}
\begin{proof}The claim follows by induction whence considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
which is also sometimes called Caldero-Chapoton map.

Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$. But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$. Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$. In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side. Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$. By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this bundle down) and thus itself trivial as a vector bundle over an affine space.

@@

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows for instance by induction when applying BGP-reflections.
\end{proof}
\begin{lemma}\label{AR}
Let $m\geq 3$ and $n\geq k\geq 2$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
\begin{enumerate}
\item There exists a short exact sequence 
\[\ses{\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}}{\tilde P_{m,k}}{\tau\tilde P_{m+1}^{(k)}}\]
where $\tau$ denotes the Auslander-Reiten translate where
$\tau\tilde P_{m+1}^{(k)}=\tilde P_{m-1}^{(k)}$. 
\item Moreover, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\cong \Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$. 
\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$.
%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Actually, we have $(\mathcal  S \tilde P_m)^t=\tilde P_{m+1}$ where $(\quad)^t$ is the functor induced by turning around the arrows (or taking the transpose representation). This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$. In this case, the first statement is straightforward as well as the third one (insert a diagram).

@@

 \[\xymatrix{0\ar[r] &P(m,k)\ar[r] &  \tilde P_{m,k}\ar[r] & \tau\tilde P_{m+1}^{(k)}\ar[r] & 0 \\
  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
Using this notation, we obtain:
\begin{lemma}\label{quotient}
 Consider the non-split short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. Then we have:
\begin{enumerate}
\item The fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is empty if and only if $U\in\Psi^{-1}_2(V,0)$, i.e. $U$ is already a subrepresentation of $P(m,k)$.
\item If the fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$.
\end{enumerate} 
\end{lemma}
\begin{proof}
If $W=0$, we get an exact sequence
\[\ses{\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)}{\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)}{\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})}.\]
Since $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we have $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$. This yields $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ which means that the induced map
\[\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\]
is zero. This means that the induced exact sequence splits. On the other hand, every subrepresentation $U\subset \tilde P_{m,k}$ such that $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty comes with a commutative diagram
 \[\xymatrix{0\ar[r] &\tilde P_{m,k}\ar[r] &  \tilde P_{m+1}^{(k-1)}\ar[r] & \tilde P_{m+1}^{(k)}\ar[r] & 0 \\
  0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m+1}^{(k)}\ar[r]\ar[u]& 0}\]
which means that the induced sequence in $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ does not split. This yields that the fibre is empty.

@@

By Lemma \ref{AR}, we have $\Hom(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})=0$ and $\Ext(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ and $\Hom(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=0$ and thus $P(m,k)\in (\tilde P_{m+1}^{(k)})^\perp$. Since this means $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we get $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$. Together with $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$, this yields the claim.

Thus it remains to show that $\Psi^{-1}_1(U,\tilde P_{m+1}^{(k)})$ is not empty if $W\neq 0$. Since $\Ext(\tilde P_{m+1}^{(k)},\tilde P_m/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ is surjective which already means that there exists a commutative diagram as above which, in turn, means that the fiber is not empty.
\end{proof}
Now we are able to state the following result concerning the fibers of $\Psi_1$:
\begin{proposition}\label{fibers}\footnote{maybe formulate this in terms of $\Psi$ (see below)}
 The following hold:
  \begin{enumerate}
    \item For $V\subsetneq \tilde P_{m+1}^{(k)}$ and $U\subseteq\tilde P_{m,k}$, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
    \item If $V=\tilde P_{m+1}^{(k)}$, the fiber $\Psi_1^{-1}(U,V)$ is not empty if and only if $\Psi_2(U)\neq (U,0)$. In this case, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
		\item Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
  \end{enumerate}
\end{proposition}
\begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective. But the representation $\tilde P_{m,k}/U$ is not as a quotient of a preprojective representation unless $U=0$. Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$. If $U=0$, we have $\Ext(V,\tilde P_{m,k})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to some $\tilde P_l$ with $l\leq m$.

@@

For the third statement, we proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
\[\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]

By Lemma \ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition. The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$. In all other cases, the fiber dimension only depend on the dimension vector $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional)}. Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell. In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.
\end{proof}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique. On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$. In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]

Using this notation, we obtain the following lemma:
\begin{lemma}
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal;
    \item All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement should directly follow from \cite{gab} and the fact that $F_Q$ is a covering functor (precise reference). The second part follows for instance recursively by applying BGP-reflections.

@@

\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k})}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not. Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason. Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom sequence does not split.
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

\end{proof}
If we choose subset $\{i_1,\ldots,i_k\}=\{1,\ldots,k\}$, we denote the cokernel simply by $\tilde P_m^{(k)}$ and $\tilde P_m^{(0)}=\tilde P_m$ respectively.

\begin{lemma}\label{directsums}
  If the quiver Grassmannians $Gr^{\tilde Q}_\tbfe(\tilde P_{m})$ and $Gr^{\tilde Q}_\tbfe(\tilde P_{m-1})$ have cell decompositions into affine spaces, then we have that $Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^s\tilde P^{t_j}_{m-1,i_j}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$ has a cell decomposition into affine spaces where $l_j,t_j\geq 1$ and $s,k\leq n$.
\end{lemma}
\begin{proof}The claim follows by induction when considering the map $$\Psi:Gr^{\tilde Q}_\tbfe(\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})\to\bigsqcup_{\tbff+\tbfg=\tbfe}  Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}),\,U\mapsto (U\cap \tilde P_{m-1,i_1},\pi(U))$$
which is also sometimes called Caldero-Chapoton map.

Indeed, we can use the fact that every subrepresentation $U$ of $\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j}$ is preprojective whence every proper factor $\tilde P_{m,i_1}/V$ is not which means that we have $\Ext(U,\tilde P_{m,i_1}/V)=0$. But since $U$ has only direct summands which are isomorphic to $\tilde P_{m-k}$ for some $k\geq 0$, we also have $\Ext(U,\tilde P_{m-1,i_1})=0$. Thus by the results of \cite[Section 3]{cc} it follows that $\psi^{-1}(U,V)=\mathbb{A}^{\Sc{\udim U}{\udim \tilde P_{m-1,i_1}/V}}$ for all pairs of subrepresentations $(U,V)\in Gr^{\tilde Q}_\tbff(\tilde P_{m,i_1})\times Gr^{\tilde Q}_\tbfg(\tilde P^{l_1-1}_{m,i_1}\oplus\bigoplus_{j=1}^k\tilde P^{l_j}_{m,i_j})$. In particular, the fibres of $\Psi$ are constant over every affine cell $A$ of the right hand side. Thus we can consider the restriction of $\Psi$ to $\Psi^{-1}(A)$. By \cite[Proposition 4]{cj}, it follows that this restriction is a subbundle of a trivial bundle (write this trivial bundle down) and thus it is itself trivial as a vector bundle over an affine space.

@@

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows for instance by induction when applying BGP-reflections.
\end{proof}
\begin{lemma}\label{AR}
Let $m\geq 3$ and $n\geq k\geq 1$. Consider the short exact sequence $\ses{\tilde P_{m,k}}{\tilde P_{m+1}^{(k-1)}}{\tilde P_{m+1}^{(k)}}$. 
\begin{enumerate}
\item There exists a short exact sequence 
\[\ses{\bigoplus_{\substack{1\leq j\leq n\\j\neq k}}\tilde P_{m-1,(k,j)}\oplus \bigoplus_{j=1}^k\tilde P_{m-2,(k,k,j)}}{\tilde P_{m,k}}{\tau\tilde P_{m+1}^{(k)}}\]
where $\tau$ denotes the Auslander-Reiten translate where
$\tau\tilde P_{m+1}^{(k)}=\tilde P_{m-1}^{(k)}$. 
\item Moreover, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\cong \Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=\kk$, $\Hom(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})=0$. 
\item We have $\tau\tilde P_{m+1}^{(k)}\in ~^\perp(\tilde P_{m+1}^{(k)})$.
%\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
\end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
We have $\mathcal  S \tilde P_m=\tilde P_{m+1}$ (up to permutation). This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_2$. In this case, the first statement is straightforward as well as the third one (insert a diagram).

@@

 \[\xymatrix{0\ar[r] &P(m,k)\ar[r] &  \tilde P_{m,k}\ar[r] & \tau\tilde P_{m+1}^{(k)}\ar[r] & 0 \\
  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
By $\Psi_2$ we denote the corresponding map of quiver Grassmannians.
Using this notation, we obtain:
\begin{lemma}\label{quotient}
\begin{enumerate}
\item The fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is empty if and only if $U\in\Psi^{-1}_2(V,0)$, i.e. $U$ is already a subrepresentation of $P(m,k)$.
\item If the fibre $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty, we have $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$.
\end{enumerate} 
\end{lemma}
\begin{proof}
If $W=0$, we get an exact sequence
\[\ses{\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)}{\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)}{\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)})}.\]

By Lemma \ref{AR}, we have $\Hom(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})=0$, $\Ext(\tilde P_{m+1}^{(k)},\tau \tilde P_{m+1}^{(k)})\cong\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=\kk$ and $\Hom(\tilde P_{m+1}^{(k)},\tilde P_{m,k})=0$ and thus $P(m,k)\in (\tilde P_{m+1}^{(k)})^\perp$. Since this means $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$, we get $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$. This yields $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)\cong\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m,k})=\kk$ which means that the induced map
\[\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})\]
is zero. Therefore, the induced exact sequence splits. On the other hand, every subrepresentation $U\subset \tilde P_{m,k}$ such that $\Psi_1^{-1}(U,\tilde P_{m+1}^{(k)})$ is not empty comes with a commutative diagram
 \[\xymatrix{0\ar[r] &\tilde P_{m,k}\ar[r] &  \tilde P_{m+1}^{(k-1)}\ar[r] & \tilde P_{m+1}^{(k)}\ar[r] & 0 \\
  0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m+1}^{(k)}\ar[r]\ar[u]& 0}\]
which means that the induced sequence in $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ does not split. This yields that the fibre is empty.

@@

Again we can apply Lemma \ref{AR} in order to see that $\Ext(\tilde P_{m+1}^{(k)},P(m,k)/V)=0$ as $\Ext(\tilde P_{m+1}^{(k)},P(m,k))=0$. 
 Together with $\Ext(\tilde P_{m+1}^{(k)},\tau\tilde P_{m+1}^{(k)}/W)=0$, this yields the claim.

Thus it remains to show that $\Psi^{-1}_1(U,\tilde P_{m+1}^{(k)})$ is not empty if $W\neq 0$. Since $\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k}/U)= 0$, we can conclude that the map $\Ext(\tilde P_{m+1}^{(k)},U)\to\Ext(\tilde P_{m+1}^{(k)},\tilde P_{m,k})$ is surjective which already means that there exists a commutative diagram as above which, in turn, means that the fiber is not empty.
\end{proof}
Now we are able to state the following result concerning the fibers of $\Psi_1$:
\begin{proposition}\label{fibers}\footnote{maybe formulate this in terms of $\Psi$ (see below)}
 The following hold:
  \begin{enumerate}
    \item For $V\subsetneq \tilde P_{m+1}^{(k)}$ and $U\subseteq\tilde P_{m,k}$, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.
    \item If $V=\tilde P_{m+1}^{(k)}$, the fiber $\Psi_1^{-1}(U,V)$ is not empty if and only if $\Psi_2(U)\neq (U,0)$. In this case, we have $\Psi_1^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,k}/U\rangle}$.

  \end{enumerate}
\end{proposition}
\begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective. But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$. Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$. If $U=0$, we have $\Ext(V,\tilde P_{m,k})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to some $\tilde P_l$ with $l\leq m$.

@@

\end{proof}
\begin{theorem}\label{cellscover}
Every quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
We proceed by induction and combine the two maps $\Psi_1$ and $\Psi_2$ and obtain a map
\[\Psi:Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})\to\bigsqcup_{\tbff+\tbfg+\tbfh=\tbfe} Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)}).\]

By Lemma \ref{directsums} and induction hypothesis every quiver Grassmannian on the right hand side has a cell decomposition. The second part of the Proposition says that the fibres are empty if and only if $\tbfg=0$ and $\tbfh=\udim \tilde P_{m+1}^{(k)}$. In all other cases, the fiber dimension only depend on the dimension vectors $\tbff, \tbfg,\tbfh$ which means that they are constant over $Gr^{\tilde Q}_\tbff( P(m,k))\times Gr^{\tilde Q}_\tbfg(\tau\tilde P_{m+1}^{(k)})\times Gr^{\tilde Q}_\tbfh(\tilde P_{m+1}^{(k)})$\footnote{actually this should already say that this is a vector bundle as the base space is smooth (all reps are exceptional)}. Analogously to Lemma \ref{directsums}, we can conclude that this induces trivial bundles over every affine cell. In total, this yields a cell decomposition of the quiver Grassmannian $Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^{(k-1)})$.

\end{proof}

Note that we can also consider 
$\Psi_1:Gr^{\tilde Q}_\tbfe(\tilde P^{(k-1)}_{m})\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^{k}\tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$ where $\tilde P_m^{(n-1)}=\tilde P_{m-1}^{(1)}$ (up to renumbering the arrows). But then one needs to adjust $\Psi_2$ because the factor of $\bigoplus_{i=1}^{k}\tilde P_{m-1,i}$ were $(\tau\tilde P_m^{(k)})^k$.
